Supplementary Information: Tropical tree drought sensitivity is jointly shaped by drought characteristics, species adaptations, and individual microenvironments

### 2025-06-18 doc/supplementary_information.Rmd
updates to supplementary figures and appendix

![**Figure S10:** Testing correlations of variables across all individuals](display/explore/cond_dep_alltrees.png)

@@

@@

>>>>

![**Figure S10:** Testing correlations of variables across all individuals](display/cond_dep_alltrees.png)

@@

## Visualising sensitivity with predictors

![](display/sens_var_rels.png)

## Alternate models using Topographic Position Index

As an alternate measure of wetness to Topographic Wetness Index (TWI) that requires the total upslope area, we used Topographic Position Index (TPI), a localised convexity/concavity-based metric of water availability as a predictor.
We calculated TPI using the package *spatialEco* [@evans_spatialeco_2023] using a circular buffer window of 1, 3, 5 and 7 pixels. 
Larger window sizes while providing a smoother surface on the plot, clip out larger portions of the plot margin where the window might bleed outside. 
We chose to use the 5-pixel version because of the balance between smoothness across the landscape and data loss.

TPI and TWI had better resolution in different parts of the wetness gradient, with TWI capturing larger resolution among wetter locations and TPI capturing larger resolution among drier locations. 
Interaction models of deciduousness with TPI showed qualitatively similar results with the TWI models across the three drought years.

![](display/FigSI_TPI_preds.png)

Similarly, models accounting for DBH and CII showed similar directional effects of wetness whether TWI or TPI was used. 
Please note that left to right represents wet to dry, given the way that TPI is calculated.

![](display/Fig4_tpi_3yrs.png)

@@

# References {-}
